Using tours to visually investigate properties of new projection pursuit indexes with application to problems in physics

### 2019-08-06 scagnostics.Rmd
Github references

This article was created with R Markdown [@rmarkdown], the code for the paper is available at [XXX].
The functions for testing new index functions as presented in this work are implemented in the R package spinebil [XXX].
The R package galahr [XXX] provides a graphical interface to the tourr package allowing for interactive exploration using the guided tour.
Additional information in the appendix is XXX

>>>>

This article was created with R Markdown [@rmarkdown], the code for the paper is available at [@paperSRC].
The functions for testing new index functions as presented in this work are implemented in the R package spinebil [@spinebil].
The R package galahr [@galahr] provides a graphical interface to the tourr package allowing for interactive exploration using the guided tour.
Additional information in the appendix is XXX
